### 2018-08-03 paper/finitecomplete-failures.tex
update

% ==========================================================================
\section{Finite Complete Test Suites for CSP Failures Refinment}
\label{sec:finitecompletefails}
% ==========================================================================

>>>>

% ==========================================================================
\section{Finite Complete Test Suites for CSP Failures Refinement}
\label{sec:finitecompletefails}
% ==========================================================================

Given a finite-state CSP process $P$ and its normalised transition graph 
\[
G(P) = ( N, \ii n, \Sigma, t : N\times\Sigma \pfun N, r : N \fun \mathbb{P}\mathbb{P}(\Sigma)),
\]
suppose that $V\subseteq\Sigma^*$ is a 
prefix-closed set  of sequences of events. By $t(\ii n,V)$ we denote the set
\[
t(\ii n,V) = \{ n\in N~|~\exists s\in V: s\in\trc(P)\wedge G(P)/s = n \}
\] 
of nodes in $N$ that are reachable in $G(P)$ by applying traces of $V$.

\begin{lemma}
\label{lemma:extendV}
Let $P$ be a CSP process with normalised transition graph $G(P)$, 
such that all states in $N$ are reachable.
Let $V\subseteq\Sigma^*$ be a finite prefix-closed set of
sequences of events. Suppose that  $G(P)$ reaches $k < |N|$ nodes under $V$, that is,
$|t(\ii n,V)| = k$. Let $V.\Sigma$ denote the set of all sequences from $V$, extended by an event of $\Sigma$.
Then $G(P)$ reaches at least $(k+1)$ nodes under $V\cup V.\Sigma$.
\end{lemma}
\begin{proof}
Suppose that $n'\in (N - t(\ii n,V))$.  Since all nodes in $N$ are reachable, there exists
a trace $s$ such that $G(P)/s = n'$. Decompose $s = s_1.e.s_2$ with $s_i\in\Sigma^*, e\in\Sigma$, such that $G(P)/s_1 \in t(\ii n,V)$ and $G(P)/s_1.e \not\in t(\ii n,V)$. Such a decomposition always exists, because $V$ is prefix-closed and therefore contains the empty trace $\varepsilon$. Note, however, that it is not necessarily the case that $s_1\in V$.

Since $G(P)$ reaches $G(P)/s_1$ under $V$, there exists a trace $u\in V$ such that
$\ol n = G(P)/u = G(P)/s_1$. Since $s = s_1.e.s_2$ is a trace of $P$ and $n = G(P)/s_1$,
$(\ol u,e)$ is in the domain of $t$, therefore,  
$n = G(P)/u.e = G(P)/s_1.e \not\in t(\ii n,V)$ is a well-defined node
of $N$ which is not contained in $t(\ii n,V)$. Since $u.e\in V\cup V.\Sigma$,
$G(P)$ reaches at least the additional node $n$ under $V\cup V.\Sigma$. This completes the proof.
\xbox
\end{proof}

% ==========================================================================
\subsection{Test Cases for Verifying CSP Failures Refinement}

For a given reference process $P$ and for each $n\ge 0$, 
we define a CSP test process as follows. 
\begin{eqnarray}
U_F(n) & = & U_F(n,\varepsilon)
\\
U_F(n,s) & = & \big( e:(\Sigma - [P/s]^0) \then \dag\then \Skip \big)
\label{eq:ufa}
\\ & & \extchoice \nonumber
\\ & & ([P/s]^0 = \varnothing)    \&   \big( \omega \then \Skip \big)
\label{eq:ufb}
\\ & & \extchoice \nonumber
\\ & & (\#s < n) \& \big( e:[P/s]^0 \then U_F(n,s.e) \big)
\label{eq:ufc}
\\ & & \extchoice \nonumber
\\ & & (\#s = n) \& \big( \sqcap_{H\in\text{MINHIT}(P/s)} ( e:H \then \omega \then\Skip   )  \big)
\label{eq:ufd}
\end{eqnarray}

A test is performed by running $U_F(n)$ concurrently with any SUT process $Q$
that operates on the same alphabet as $P$, synchronising over
alphabet $\Sigma$. Therefore, a test execution is any trace of the concurrent process
\[
Q\parallel[\Sigma] U_F(n).
\]
It is assumed that the events $\dag$ and $\omega$ denoting FAIL and PASS of the test execution, respectively, are events outside $\Sigma$.
Since we assume that $Q$ is free of livelocks, it is guaranteed that each test execution terminates after some $s\in\trc(P)$ with length $(n+1)$ at the latest. 
The test is \emph{passed} by the SUT (we write $Q\ \pass\ U(n)$) if and only if {\it every} execution of $Q\parallel[\Sigma] U_F(n)$ terminates with PASS event $\omega$. This can also be  expressed by means of a trace equivalence relation:
\[
Q\ \pass\ U(n) \equiv  (Q\parallel[\Sigma] U_F(n)) \hide \Sigma =_T (\omega\then\Skip)
\]
This type of pass relation is often called \emph{must test}, because every test execution must end with the PASS event $\omega$ \cite{Hennessy:1988:ATP:50497}.

Intuitively speaking, $U_F(n)$ is able to perform any trace $s$ of $P$, 
up to a length of $n$. If, after having already run through $s\in\trc(P)$ with $\#s < n$,
an event is accepted by the SUT which is outside the initials of $P/s$, the test 
immediately terminates with FAIL-event $\dag$. This is handled by the first operand of the
external choice in sub-process $U(n,s)$.

If $P/s$ is the STOP-process, this is revealed by its initials being empty. In this case, the test may terminate 
successfully (second operand of the external choice in $U(n,s)$). Note that at the same time, any (now illegal) event of the alphabet is also accepted by the test.
Therefore,
if the SUT would still accept an event in a state where $P/s$ is supposed to have stopped, there exists a test execution which terminates with FAIL by choosing the first
operand of the external choice.

If the length of $s$ is still less than $n$, the test accepts any event from the initials
$[P/s]^0$ and continues recursively as sub-process $U(n,s.e)$ (third operand of the external choice). A test of this type is called \emph{adaptive}, because it accepts any legal behaviour of the SUT and adapts its consecutive behaviour to the event selected by the SUT.

After having  run successfully 
through a trace of length $n$, the test changes its behaviour:
instead of offering {\it all} legal events from $[P/s]^0$ to the SUT, 
it nondeterministically chooses 
a minimal hitting set of $\minaccs(P/s)$ and only offers the events contained in this set.
If the SUT refuses to engage into any of these events, this reveals a violation of the
failures refinement: according to Lemma~\ref{lemma:hseta}, a conforming SUT should accept
at least one event of each minimal hitting set in $\text{MINHIT}(P/s)$. Therefore, the test
only terminates with success $\omega$, if such an event is accepted by the SUT.

After this informal explanation of tests representing adaptive test cases, we are ready to prove the main theorem of this paper.

\begin{theorem}
Let $P$ be a divergence-free CSP process over alphabet $\Sigma$ 
whose normalised transition graph $G(P)$ has $n$ states. Define fault domain ${\cal D}$ as
the set of all divergence-free CSP processes over alphabet $\Sigma$, whose transition graph
has at most $m$ states with $m \ge n$. 
Then the test suite 
\[
\TS_F = \{ U_F(k)~|~0 \le k \le nm  \}
\]
is complete with respect to ${\cal F} = (P,\lessdet_F,{\cal D})$.
\end{theorem}
\begin{proof}
To prove soundness of $\TS_F$, suppose that $Q\in{\cal D} \wedge P\lessdet_F Q$. Then
$\trc(Q)\subseteq \trc(P)$, and Lemma~\ref{lemma:hseta} implies that 
for all traces $s$ of $Q$, every $H\in\text{MINHIT}(P/s)$ is a 
    hitting set for $\minaccs(Q/s)$. As a consequence, when running in parallel
with $Q$, any adaptive test $U_F(n)$ will always enter the branches 
(\ref{eq:ufb}), (\ref{eq:ufc}),  or (\ref{eq:ufd}) of the external choice construction
for $U_F(n,s)$. Branch (\ref{eq:ufb}) always leads to a PASS verdict, branch (\ref{eq:ufc})
always to test continuation without a verdict. For the last branch, we note that 
any selected minimal hitting set $H\in\text{MINHIT}(P/s)$ has a non-empty intersection with
each of the minimal acceptances of $Q/s$. As a consequence, $Q/s$ will never block when offered events from $H$, and the test terminates with PASS event $\omega$. Note that this argument requires that $Q$ is free of livelocks, because otherwise the PASS-events might not become visible, due to unbounded sequences of hidden events performed by $Q$. Note further, that this proof did not refer in any way to the size of $Q$'s normalised transition graph, so the test suite is sound for {\it all} non-divergent CSP process refining $P$.

To prove exhaustiveness, consider a process $Q\in{\cal D}$ with $P\not\lessdet_F Q$. This non-conformance can be caused in two possible ways.
\begin{enumerate}
\item $\trc(Q)\not\subseteq \trc(P)$
\item There exists a joint trace $s\in\trc(Q)\cap\trc(P)$ and a minimal acceptance $A_Q$
of $\minaccs(Q/s)$, such that 
(see Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb})).
\[
\forall A_P\in\minaccs(P/s): A_P\not\subseteq A_Q,
\] 
\end{enumerate}
It has to be shown for each of the two possibilities that at least one test execution of some $(Q\parallel[\Sigma] U(k))$ with $k\le nm$ ends with the FAIL event $\dag$.
\xbox
\end{proof}

### 2018-08-03 paper/preliminaries.tex
update

@@

By $[n]^0$ we denote the \emph{fan-out} of $n$:~the set of events occurring
as labels in any outgoing transitions.
$$
[n]^0 = \{ e\in\Sigma~|~(n,e)\in\dom~t \}
$$
We also use this notation for CSP processes:~$[P]^0$ is the set
of events $P$ may engage into, in other words, the initials of $P$ after the
empty trace of events, that is, $initials(P/\langle\rangle)$ as defined
in~\cite{Roscoe2010}.

@@

For finite CSP processes, since the refusals of each process state are
subset-closed~\cite{Hoare:1985:CSP:3921,Roscoe2010}, $\refs(P/s)$ can be
re-constructed by knowing the set of \emph{maximal refusals}
$\maxrefs(P/s)\subseteq\refs(P/s)$. More formally, the maximal refusals
$\maxrefs(P/s)$ are defined as
$$
\maxrefs(P/s) = \{ R \in\refs(P/s)~|~\forall R'\in \refs(P/s) - \{ R\}: R \not\subseteq R'\}
$$
Conversely, with the maximal refusals at hand, we can reconstruct the refusals by subset-closure:
$$
\refs(P/s) = \{ R'\in\power(\Sigma)~|~\exists R\in \maxrefs(P/s): R'\subseteq R \}.
$$
To see that this approach works only for finite CSP processes, consider the
example where $\Sigma$ is infinite. In this case,
$\maxrefs(STOP/\langle\rangle)$ is empty, and so we cannot use this set to
calculate the refusals of $STOP$, that is, $\refs(STOP/\langle\rangle)$ as
defined above. As with refusals, we also use the transition graph-oriented
notation $\maxrefs(n) \subseteq r(n)$ to denote the maximal refusals
associated with graph state $n$: if $n$ is the state reached in the
transition graph by following the edge labels in trace $s$, then $\maxrefs(n)
= \maxrefs(P/s)$.

Well-formed normalised transition graphs must not refuse an event of the
fan-out of a state in {\it every} refusal applicable in this state; more
formally,
\begin{equation}
\label{eq:wellformedg}
\forall n\in N, e\in\Sigma: (n,e)\in\dom~t \Rightarrow
\exists R\in \maxrefs(n): e\not\in R
\end{equation}
%The total function $a$ maps each node to its set of \emph{minimal acceptances}:
%if $n\in N$ corresponds to a deterministic process state of $P$, $ac(n)$ contains a single acceptance $A\subseteq \Sigma$, and every $e\in A$ is in one-one-correspondence with a transition $t(n,e)$. If $n$ corresponds to a nondeterministic process state, $ac(n)$ contains at least two acceptances $A_1, A_2, \dots, A_k$. This reflects the fact that in a nondeterministic state, $P$ must accept all events of one acceptance
%$A_i, i \in \{ 1,\dots,k\}$, but may refuse all events $e$ from
%$A_j \setminus A_i, j\neq i$.
%
%Each well-defined transition graph $G(P)$ fulfils the following condition. The union of all minimal acceptances in each node corresponds to the set of events labelling its outgoing transitions.
%\begin{equation}
%\label{eq:wellformedg}
%\forall n\in N: (n,e)\in\dom~t \Leftrightarrow e\in\bigcup ac(n)
%\end{equation}
%In this condition, $\dom~t$ denotes the domain of function $t$.
By construction, normalised transition graphs reflect the \emph{failures
semantics} of finite-state CSP processes:~the traces $s$ of a process are the
sequences of transition associated with paths through the graph,
starting at $\ii n$. The pairs $(s,R)$ with $s\in\trc(P)$ and $R\in
r(G(P)/s)$ represent the failures $\failure(P)$ of $P$.

@@

\begin{lemma}
\label{lemma:tgtrcref}
\begin{eqnarray}
P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
\label{eq:trcrefa}
\\
\label{eq:failrefa}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {}
\\ & & \forall s\in\trc(G(Q)), R_Q\in\maxrefs(G(Q)/s): 
\\ & & \tabd
\exists R_P\in\maxrefs(G(P)/s): R_Q\subseteq R_P
\\
\label{eq:failrefb}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {}
\\ & & \forall s\in\trc(G(Q)), A_Q\in\minaccs(G(Q)/s):
\\ & & \tabd
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\end{eqnarray}
\end{lemma}

@@

\begin{lemma}
\label{lemma:hseta}
Let $P, Q$ be two finite-state CSP processes satisfying $P\lessdet_T Q$. 
For each $s\in\trc(P)$,
let $\text{MINHIT}(s)$ denote the
collection of all minimal hitting sets of $\minaccs(P/s)$. 
Then the following statements are equivalent.
\begin{enumerate}
\item $P\lessdet_F Q$
\item For all $s\in\trc(P)\cap \trc(Q)$ and $H \in  \text{MINHIT}(s)$, $H$ is
a (not necessariliy minimal) hitting set of $\minaccs(Q/s)$.
\end{enumerate}
\end{lemma}
\begin{proof}
For showing ``$1 \Rightarrow 2$'', assume that $P\lessdet_F Q$ and suppose that
$s\in\trc(P)\cap \trc(Q)$. Then Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), implies that 
\[
\forall A_Q\in\minaccs(G(Q)/s):
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\]
Therefore, every minimal acceptance set $A_Q\in\minaccs(G(Q)/s)$ contains a
minimal acceptance set from  \minaccs(G(P)/s). As a consequence, any hitting set
$H \in  \text{MINHIT}(s)$ also has a non-empty intersection with every 
$A_Q\in\minaccs(G(Q)/s)$.

To prove ``$2 \Rightarrow 1$'',
assume $P\lessdet_T Q$, but $P\not\lessdet_F Q$. According to Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), there exists $s\in\trc(P)\cap \trc(Q)$ such that 
\[
\exists A_Q\in\minaccs(G(Q)/s): \forall A_P\in\minaccs(G(P)/s): A_P\not\subseteq A_Q (*)
\]
Define 
\[
\overline H = \bigcup_{A_P\in\minaccs(G(P)/s)} \big( A_P \setminus A_Q \big).
\]
Since $A_P \setminus A_Q \neq\varnothing$ because of (*), $\overline H$ is a hitting set
of $\minaccs(G(P)/s)$ which has a non-empty intersection with $A_Q$. Minimising 
$\overline H$ induces the existence
of a minimal hitting set $H\in \text{MINHIT}(s)$ which is {\it not} a hitting set of 
of $\minaccs(G(Q)/s)$. This completes the proof of the lemma.
\xbox
\end{proof}

>>>>

Throughout this paper, the alphabet of CSP processes $P$ is denoted by $\Sigma$. 
Since we are only considering ``classical'' CSP processes, the alphabet is always finite.

@@

By $[n]^0$ we denote the \emph{initials} of $n$:~the set of events occurring
as labels in any outgoing transitions.
$$
[n]^0 = \{ e\in\Sigma~|~(n,e)\in\dom~t \}
$$
We also use this notation for CSP processes:~$[P]^0$ is the set
of events $P$ may engage into, in other words, the initials of $P$ after the
empty trace of events, that is, $initials(P/\langle\rangle)$ as defined
in~\cite{Roscoe2010}.

@@

For finite CSP processes, since the refusals of each process state are
subset-closed~\cite{Hoare:1985:CSP:3921,Roscoe2010}, $\refs(P/s)$ can be
re-constructed by knowing the set of \emph{maximal refusals}
$\maxrefs(P/s)\subseteq\refs(P/s)$. More formally, the maximal refusals
$\maxrefs(P/s)$ are defined as
\begin{equation}
\maxrefs(P/s) = \{ R \in\refs(P/s)~|~\forall R'\in \refs(P/s) - \{ R\}: R \not\subseteq R'\}
\end{equation}
Conversely, with the maximal refusals at hand, we can reconstruct the refusals by subset-closure:
\begin{equation}
\refs(P/s) = \{ R'\in\power(\Sigma)~|~\exists R\in \maxrefs(P/s): R'\subseteq R \}.
\end{equation}
To see that this approach works only for finite CSP processes, consider the
example where $\Sigma$ is infinite. In this case,
$\maxrefs(STOP/\langle\rangle)$ is empty, and so we cannot use this set to
calculate the refusals of $STOP$, that is, $\refs(STOP/\langle\rangle)$ as
defined above. As with refusals, we also use the transition graph-oriented
notation $\maxrefs(n) \subseteq r(n)$ to denote the maximal refusals
associated with graph state $n$: if $n$ is the state reached in the
transition graph by following the edge labels in trace $s$, then $\maxrefs(n)
= \maxrefs(P/s)$.

Well-formed normalised transition graphs must not refuse an event of the
fan-out of a state in {\it every} refusal applicable in this state; more
formally,
\begin{equation}
\label{eq:wellformedg}
\forall n\in N, e\in\Sigma: (n,e)\in\dom~t \Rightarrow
\exists R\in \maxrefs(n): e\not\in R
\end{equation}

By construction, normalised transition graphs reflect the \emph{failures
semantics} of finite-state CSP processes:~the traces $s$ of a process are the
sequences of transition associated with paths through the graph,
starting at $\ii n$. The pairs $(s,R)$ with $s\in\trc(P)$ and $R\in
r(G(P)/s)$ represent the failures $\failure(P)$ of $P$.

When investigating  tests for failures refinement, 
the notion of \emph{acceptances}~\cite{Hennessy:1988:ATP:50497} 
which is dual to refusals will also be useful. An acceptance set of $P/s$ is a subset
of the initials $[P/s]^0$, i.e. a subset of events labelling  outgoing transitions
of $G(P)/s$. If the behaviour of  $P/s$ is deterministic, its only acceptance equals
$[P/s]^0$, because $P/s$ will never refuse any of the events contained in this set. If
$P/s$ is nondeterministic, it will internally choose one of it 
\emph{minimal acceptance sets} $A$ and never refuse any event in $A$, while refusing the
events in $\Sigma-A$. The acceptances of 
 $P/s$ are denoted by $\accs(P/s)$, the minimal acceptances by $\minaccs(P/s)$. 
 They fulfil the following rules.
\begin{eqnarray}
A\in \minaccs(P/s) & \Leftrightarrow & \exists R\in\maxrefs(P/s) \wedge A = \Sigma-R
\label{eq:accref}
\\
\bigcup \{ A~|~A\in \accs(P/s)\} & = & [P/s]^0
\label{eq:accinitials}
\\
 X\in\accs(P/s) &\Leftrightarrow & A\in \minaccs(P/s) \wedge A\subseteq X \subseteq [P/s]^0
 \label{eq:accsubset}
\end{eqnarray} 
Note that (\ref{eq:accref}) can be regarded as a definition of minimal acceptances by means
of maximal refusals. Then (\ref{eq:accinitials}) and (\ref{eq:accsubset}) are consequences
of this definition and  the fact that refusals are subset-closed.

Every node of a transition graph can be labelled with with its minimal acceptances, and this information is equivalent to 
that contained in its maximal refusals.

@@

\begin{lemma}
\label{lemma:tgtrcref}
\begin{eqnarray}
P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
\label{eq:trcrefa}
\\
\label{eq:failrefa}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {} \nonumber
\\ & & \forall s\in\trc(G(Q)), R_Q\in\maxrefs(G(Q)/s):  \nonumber
\\ & & \tabd
\exists R_P\in\maxrefs(G(P)/s): R_Q\subseteq R_P
\\
\label{eq:failrefb}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {} \nonumber
\\ & & \forall s\in\trc(G(Q)), A_Q\in\minaccs(G(Q)/s): \nonumber
\\ & & \tabd
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\end{eqnarray}
\end{lemma}

For proving our main theorems, it is necessary to consider the \emph{product} of 
normalised transition graphs. We need this only for the investigation of corresponding traces in reference processes and processes under test. Therefore, the 
labelling of nodes with maximal refusals or minimal acceptances   will be disregard in the 
product construction.
Consider two normalised transition graphs 
\[
G_i = ( N_i, \ii n_i, \Sigma, t_i : N_i\times\Sigma \pfun N_i, r_i : N_i \fun \mathbb{P}\mathbb{P}(\Sigma)),\qquad i = 1,2,
\]
over the same alphabet $\Sigma$. Then their product is defined by
\begin{eqnarray}
G_1\times G_2 & = & (N_1\times N_2,(\ii n_1,\ii n_2), t:(N_1\times N_2)\times\Sigma\pfun (N_1\times N_2))
\\
\dom~t & = & \{ ((n_1,n_2),e)\in (N_1\times N_2)\times\Sigma~|   \nonumber
\\ & & \tabc
(n_1,e)\in\dom~t_1\wedge 
(n_2,e) \in\dom~t_2    \}
\\
t((n_1,n_2),e) & = & (t_1(n_1,e),t_2(n_2,e))\ \text{for $((n_1,n_2),e)\in\dom~t$}
\end{eqnarray}

@@

\begin{lemma}
\label{lemma:hseta}
Let $P, Q$ be two finite-state CSP processes satisfying $P\lessdet_T Q$. 
For each $s\in\trc(P)$,
let $\text{MINHIT}(P/s)$ denote the
collection of all minimal hitting sets of $\minaccs(P/s)$. 
Then the following statements are equivalent.
\begin{enumerate}
\item $P\lessdet_F Q$
\item For all $s\in\trc(P)\cap \trc(Q)$ and $H \in  \text{MINHIT}(P/s)$, $H$ is
a (not necessariliy minimal) hitting set of $\minaccs(Q/s)$.
\end{enumerate}
\end{lemma}
\begin{proof}
For showing ``$1 \Rightarrow 2$'', assume that $P\lessdet_F Q$ and suppose that
$s\in\trc(P)\cap \trc(Q)$. Then Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), 
states that 
\[
\forall A_Q\in\minaccs(G(Q)/s):
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\]
Therefore,
$H \in  \text{MINHIT}(P/s)$ not only implies $H\cap A_P\neq\varnothing$ for all minimal
acceptances $A_P$, but also
$H\cap A_Q\neq\varnothing$ for every minimal acceptance $A_Q$, because $A_P\subseteq A_Q$ for at least one $A_P$. As a consequence, each $H \in  \text{MINHIT}(P/s)$ is also a hitting set for $\minaccs(G(Q)/s)$.

To prove ``$2 \Rightarrow 1$'',
assume $P\lessdet_T Q$, but $P\not\lessdet_F Q$. According to Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), there exists $s\in\trc(P)\cap \trc(Q)$ such that 
\[
\exists A_Q\in\minaccs(G(Q)/s): \forall A_P\in\minaccs(G(P)/s): A_P\not\subseteq A_Q 
\qquad (*)
\]
Define 
\[
\overline H = \bigcup\{ A_P \setminus A_Q~|~A_P\in\minaccs(G(P)/s) \}.
\]
Since $A_P \setminus A_Q \neq\varnothing$ for all $A_P$ because of (*), $\overline H$ is a hitting set
of $\minaccs(G(P)/s)$ which has an  empty intersection with $A_Q$. Minimising 
$\overline H$ induces the existence
of a minimal hitting set $H\in \text{MINHIT}(P/s)$ which is {\it not} a hitting set of 
of $\minaccs(G(Q)/s)$. This completes the proof of the lemma.
\xbox
\end{proof}
